The Revisited Hidden Weight Bit Function

### 2024-12-05 RevisedHiddenWeight.tex
Removed some comments

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
		\hline
		$ n $      & $4$     & $6$     & $8$     & $10$    & $12$    & $14$    & $16$    & $18$    \\ \hline
		$(d, e)$ & $(1,2)$ & $(1,3)$ & $(1,5)$  & $(1,7)$ & $(1,9)$ & $(1,11)$ & $(1,13)$ & $(1,15)$ \\ 
		 &     &    & $(2,4)$  & $(2,6)$ & $(2,8)$ & $(2,10)$ & $(2,12)$ & $(2,14)$\\ 
		 &     &    &     & $(3,5)$ & $(3,6)$ & $(3,9)$ & $(3,11)$ & $(3,13)$\\ 
		 &     &    &     &  &  &  & $(4,9)$ & $(4,11)$\\ 
	 &     &    &     &  &  &  &  & $(5,10)$ \\ \hline
	\end{tabular}
	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.\tsnote{Aren't the roles of $d$ and $e$ reversed?}}
	\label{table:FAI}
\end{table}

\pmnote{ degree of $h$, denoted by $e$ here is always greater than the AI, whereas $\degg(g)=d$ is smaller. It is consistent}

>>>>

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
		\hline
		$ n $      & $4$     & $6$     & $8$     & $10$    & $12$    & $14$    & $16$    & $18$    \\ \hline
		$(d, e)$ & $(1,2)$ & $(1,3)$ & $(1,5)$  & $(1,7)$ & $(1,9)$ & $(1,11)$ & $(1,13)$ & $(1,15)$ \\ 
		 &     &    & $(2,4)$  & $(2,6)$ & $(2,8)$ & $(2,10)$ & $(2,12)$ & $(2,14)$\\ 
		 &     &    &     & $(3,5)$ & $(3,6)$ & $(3,9)$ & $(3,11)$ & $(3,13)$\\ 
		 &     &    &     &  &  &  & $(4,9)$ & $(4,11)$\\ 
	 &     &    &     &  &  &  &  & $(5,10)$ \\ \hline
	\end{tabular}
	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.}
	\label{table:FAI}
\end{table}
